---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dacol

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/ldanai/dacol.svg?branch=master)](https://travis-ci.org/ldanai/dacol)
[![Codecov test coverage](https://codecov.io/gh/ldanai/dacol/branch/master/graph/badge.svg)](https://codecov.io/gh/ldanai/dacol?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/dacol)](https://cran.r-project.org/package=dacol)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![DOI](https://zenodo.org/badge/123997166.svg)](https://zenodo.org/badge/latestdoi/123997166)
<!-- badges: end -->

dacol provides utilities to add or modify columns in dataframe.

The utilities include:

* Statistical measures: `mode`, `confident_interval`
* Normalize a vector column: `cosine`, `logistic`, `zscore`
* Compute distance between 2 vector columns: `euclidean`, `pearson`, `cosine`, `canberra`
* Manage outliers: `trim_outlier`, `normalize_percentile`
* Calculate percentile: `decile_band`, `decile_ptile`, `rank_ptile`

More info: https://ldanai.github.io/dacol/

## Installation

You can install dacol from github with:

``` r
# install.packages("remotes")
remotes::install_github("ldanai/dacol")
```

## Example

This shows how to use dacol:

```{r, message = FALSE}
library(dacol)
library(dplyr)

max = 30
dta1 = tibble(x1 = seq(-1.2*max, 1.2*max, length.out = 200),
              x2 = seq(0, max, length.out = 200),
              x3 = sample(200))

dta1

dta1 = 
  dta1 %>% 
  mutate(
    # Transformation
    y_cosine   = transform_cosine(x1, max),
    y_logistic = transform_logistic(x2, max),
    y_zcore    = transform_zscore(x2),
    
    # Distant between 2 vector columns
    y_dist_canb = dist_canberra(x2, x3),
    y_dist_cos  = dist_cosine(x2, y_zcore),
    y_dist_euc  = dist_euclidean(x2, y_zcore),
    y_dist_pear = dist_pearson(x2, y_zcore),
    
    # Manage outliers
    y_trim = trim_outlier(x3, 0.01),
    y_norm = normalize_percentile(x3, 0.01),
    
    # Stats measures
    y_mode = mode_stats(x3),
    
    # Band segmentation
    y_dec_band1  = decile_band(x3),
    y_dec_band2  = decile_band(x3, c(seq(0, 0.9, 0.1))),
    y_dec_ptile1 = decile_ptile(x3),
    y_dec_ptile2 = decile_ptile(x3, c(seq(0, 0.9, 0.1))),
    
    # Rank percentile
    y_ranked1 = rank_ptile(x3), 
    y_ranked2 = rank_ptile(x3, c(seq(1, 100, 1))) 
  )

dta1
```

---
Please note that the 'dacol' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
