---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# dacol

dacol provides utilities to add or modify columns into dataframe.

The utilities include:

* Statistical measures: mode, confident_interval
* Data Transformation of a vector column: cosine, logistic, zscore
* Distance between 2 vector columns: euclidean, pearson, cosine, canberra
* Data Cleasing: trim_outlier

More info: https://ldanai.github.io/dacol/
  

## Installation

You can install dacol from github with:

``` r
# install.packages("devtools")
devtools::install_github("ldanai/dacol")
```

## Example

This shows how to use dacol:

```{r, message = FALSE}
library(dacol)
library(dplyr)

max = 30
dta1 = tibble(x1 = seq(-1.2*max, 1.2*max, length.out = 200),
              x2 = seq(0, max, length.out = 200),
              x3 = sample(200))

dta1

dta1 = 
  dta1 %>% 
  mutate(
    # Transformation
    y_cosine   = transform_cosine(x1, max),
    y_logistic = transform_logistic(x2, max),
    y_zcore    = transform_zscore(x2),
    
    # Distant between 2 vector columns
    y_dist_canb = dist_canberra(x2, y_zcore),
    y_dist_cos  = dist_cosine(x2, y_zcore),
    y_dist_euc  = dist_euclidean(x2, y_zcore),
    y_dist_pear = dist_pearson(x2, y_zcore),
    
    # Manage outliers
    y_trim = trim_outlier(x3, 0.01),
    y_norm = normalize_percentile(x3, 0.01),
    
    # Stats measures
    y_mode = mode_stats(x3),
    
    # Band segmentation
    y_dec_band1  = decile_band(x3),
    y_dec_band2  = decile_band(x3, c(seq(0, 0.9, 0.1))),
    y_dec_ptile1 = decile_ptile(x3),
    y_dec_ptile2 = decile_ptile(x3, c(seq(0, 0.9, 0.1))),
    
    # Rank percentile
    y_ranked1 = rank_ptile(x3), 
    y_ranked2 = rank_ptile(x3, c(seq(1, 100, 1))) 
  )

dta1
```

